---
title: "Flu Symptoms"
output: html_notebook
---


```{r}
library(dplyr)
library(lubridate)
library(ggplot2)
```

```{r}
flu <- read.csv("data/FluSymptoms.csv", stringsAsFactors = FALSE)
```

Call 3 symptoms "the flu"
```{r}
flu <- flu %>% 
  mutate(has_flu = ifelse(sore.throat.cough + runnynose.congestion.sneezing + fever + nausea.vomiting.diarrhea >= 3, 1, 0)) %>%
  mutate(time = ymd_hms(time)) %>%
  mutate(date = as.Date(time)) %>%
  arrange(date)

# if more than one report per day, take the latest
flu <- flu %>%
  arrange(user_id, desc(time)) %>%
  distinct(user_id, date, .keep_all = TRUE)

flu %>% arrange(date)
```

Summarise by day, limit to school year (there are some strange date values) August 2009

```{r}
daily_flu <- flu %>%
  group_by(date) %>%
  summarize(flu_count = sum(has_flu, na.rm = TRUE))
daily_flu
```

Some notes:

* Symptoms reporting didn't start in earnest until second semester
* There's a strange date (year 2003). I'm removing that.
* Flu symptoms are in aggregate (e.g., runny nose + congestion + sneezing), so I'm using 3 or greater
* If a student reported symptoms more than once per day, I took the latest report


```{r}
p1 <- ggplot(daily_flu %>% filter(date > as.Date("2009-01-09")), aes(x = date, y = flu_count)) +
  geom_line() +
  labs(title = "Second Semester",
       y = "")
p1
```

```{r}
p2 <- ggplot(daily_flu %>% filter(date >= as.Date("2009-02-01") & date <= as.Date("2009-02-28")),
       aes(x = date, y = flu_count)) +
  geom_line() +
  labs(title = "February",
       y = "")
p2
```

```{r}
library(ggpubr)
p <- ggarrange(p1, p2, ncol=1)
annotate_figure(p, left = "Students Reporting 3+ Flu-Like Symptoms")
ggsave("out/flu_symptoms.png", dpi = "retina")
```

